Do return series have power-law tails with the same index?

### 2017-05-03 papers/FX/draft.tex
Corrected the proof of the monotonicity lemma.

is not monotonic. To see this we may re-write the above as

@@

\subsection{Student's t-distributed equity return}
{\red This section is incomplete unless we can show results for $b>0$. Otherwise, we can do everything for $b=0$.} 
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume {\red instead of this function one can take a symmetric \ds\ with tails
$\P(X>x)=0.5 (\kappa/(x+\kappa))^{\alpha}$. If the symmetry causes another behavior than in the previous section this would be interesting.}
{\blue our tail index is always $\alpha$, not $\nu$.}
\[
f(x; \alpha) = c(\alpha) \left(
  1 + {x^2 \over \alpha}
\right)^{-(\alpha + 1)/2}
\]
where $\alpha > 1$ and
\[
c(\alpha) = {
  \Gamma({\alpha + 1 \over 2})
  \over
  \Gamma(\alpha/2) \sqrt{\alpha \pi}
}
\]
In the same way as for \eqref{eq:ipf}, we can write $\wt u(F, \phi)$
as
\begin{eqnarray}
  && \wt u(F, \phi) \nonumber \\
  &=&
  (1 + b)
  \int_{0}^{\infty}
  \underbrace{
    {
      u(C(x)) \left[
        1 - {b \over 1 + b}\1_{\{x \ge q\}}
        \right]
      + u(C(-x))
      \over
      (K + x)^{\alpha + 1}
    }
  }_{U_{\text{all}}}
  dx
  - b u(\delta v) F_X(q)
  \label{eq:t1}
\end{eqnarray}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}. As shown in the last
section, $U_{\text{all}}$ is not monotonic when $b > 0$ and $u(\cdot)$ 
takes the power-form of \eqref{eq:hjyr}; when $b = 0$, however,
$U_{\text{all}}$ is indeed monotonic depending on the values of $\xi$
and $(1 - \phi) e^r / \phi$. In the first case, we have to resort to
numerical methods; in the 2nd case, we can find some analytic results.

@@

%% However, this is not necessarily the case when $b > 0$. For example,
%% consider the case when $q = 0$ and $\hat\phi = 1$. This may be
%% viewed an approximation to the situation where the interest rate $r$ is
%% vanishingly low while the investor is more conservative than
%% greedy. In this case we have
%% \begin{eqnarray*}
%%   \wt u(F, \phi) = \int_{0}^{\infty} e^{-b x} f(x, \alpha) dx
%% \end{eqnarray*}
%% Thus by the 1st case of lemma \ref{lemma:I} and lemma \ref{lemma:II},
%% $\opd{\alpha}\wt u(F, \phi) > 0$. In this extreme case, the investor
%% would rather seek the largest $\alpha$ or in other words, the lightest
%% tail in the market.

\subsubsection{power-utility function}
In this section we consider the case when the utility function
$u(\cdot)$ takes the form
\[
u(x) = -{1 \over \xi} x^{-\xi}
\]
One can see from figure \ref{fig:phi_hat_U_power} that both $\hat
\phi$ and $G(\alpha)$ are monotonically decreasing with $\alpha$ as in the
case of a log-utility function.
\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power.pdf}
  \end{minipage}
  \caption{$\hat\phi$ and $G(\alpha)$ when the utility
    function is $u(C) = -{2 \over \sqrt{C}}$
  }
  \label{fig:phi_hat_U_power}
\end{figure}

@@

\appendix
\section{A monontonicity lemma}
\setcounter{equation}{0}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x, \theta)$ parameterized by 
  $\theta \in \Theta$ is defined on $x \in (a, b)$,
  $a, b \in \mathbb R \cup \{-\infty, \infty\}$,
  and in addition $F(x, \theta)$ has density
  function $f(x, \theta)$ that is differentiable with respect to
  $\theta$ for all $\theta \in \Theta$.
  Moreover, $f(x, \theta)$ satisfies
  \begin{equation}\label{eq:frt}
  \int_a^b {\pd f(x, \theta) \over \pd \theta} dx
  < \infty
  \end{equation}
  Assume function $h(\cdot)$ is defined on
  $(a, b)$ and is monotonic throughout this interval;
  $X \sim F$ and $\E h(X) < \infty$. Then
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

\begin{proof}
  Firstly we show
  \[
    {\pd \over \pd \theta} \int_a^b f(x, \theta) dx
    =
    \int_a^b {\pd \over \pd \theta} f(x, \theta) dx    
  \]
  Let
  \[
  f_{\Delta}(x, \theta) = {
    f(x, \theta +  \Delta) - f(x, \theta)
    \over
    \Delta
  }
  \]
  Since $f(x, \theta)$ is differentiable for all $\theta \in \Theta$,
  \[
  f_{\Delta}(x, \theta) \to {\pd f \over \pd \theta}(x, \theta)
  \quad \Delta \to 0
  \]
  For any give $\epsilon > 0$ and sufficiently small
  $\Delta$, we have
  \[
  |f_{\Delta}(x, \theta)| <
  \left|
      {\pd f \over \pd \theta}(x, \theta)
  \right| (1 + \epsilon)
  \]
  Using \eqref{eq:frt} and dominated convergence theorem we obtain
  \[
  \lim_{\Delta \to 0} \int_a^b f_\Delta(x, \theta) dx
  =
  \int_a^b {\pd f \over \pd \theta}(x, \theta) dx
  < \infty
  \]
  That is
  \[
    {\pd \over \pd \theta} \int_a^b f(x, \theta) dx
    =
    \lim_{\Delta \to 0} {
      \int_a^b f(x, \theta + \Delta) dx
      -
      \int_a^b f(x, \theta) dx
      \over
      \Delta
    }
    =
    \int_a^b {\pd f \over \pd \theta}(x, \theta) dx     
  \]
  From \eqref{eq:frt} it easily follows that the set on which
  ${\pd f(x, \theta) \over \pd \theta} = \infty$ has Lesbegue
  measure 0. Call this set $S_0$. We have
  \begin{eqnarray*}
    && {\pd \E h(X) \over \pd \theta} \\
    &=& \int_{(a,b) \setminus S_0} h(x)
    {\pd f \over \pd \theta}(x, \theta) dx \\
    &=& \underbrace{\int_{(a, x_0) \setminus S_0}
      h(x) {\pd f \over \pd \theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{(x_0, b) \setminus S_0}
      h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_2}
  \end{eqnarray*}
  Moreover, $x_0$ being located in the interior of $(a, b)$ and
  $h(\cdot)$ being monotonic implies $h(x_0) < \infty$.
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and ${\pd f \over \pd
    \theta}(x, \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_{(a, x_0) \setminus S_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    Similarly, because ${\pd f \over \pd \theta}(x, \theta) < 0$ for
    $x \in (x_0, b)$ and $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{(x_0, b) \setminus S_0} -h(x_0)
      \left|{\pd f \over \pd \theta}(x, \theta) \right| dx
      > -h(x_0)
      \int_{(x_0, b) \setminus S_0} \left| 
        {\pd f \over \pd \theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      {\pd \E h(X) \over \pd \theta}
      > h(x_0) \int_{(a, b) \setminus S_0}
      {\pd f \over \pd \theta}(x, \theta) dx
      = h(x_0) {\partial \over \partial \theta}
      \int_{(a, b) \setminus S_0} f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    ${\pd f \over \pd \theta}(x_0, \theta) < 0$ on $(a, x_0)$  while
    ${\pd f \over \pd \theta}(x_0, \theta) > 0$ on $(x_0, b)$
    \begin{eqnarray*}
      I_1 &=&
      \int_{(a, x_0) \setminus S_0} -h(x)
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx
      >
      -h(x_0) \int_{(a, x_0) \setminus S_0}
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx
    \end{eqnarray*}
    and obviously
    \[
    I_2 > h(x_0) \int_{(x_0, b) \setminus S_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    So
    \[
    {\pd \E h(X) \over \pd \theta}
    = I_1 + I_2
    > h(x_0) {\partial \over \partial \theta}
    \int_{(a, b) \setminus S_0} f(x, \theta) dx = 0
    \]
  \end{enumerate}
\end{proof}

@@

\section{Proof of Lemma~\ref{thrm:I}}
\setcounter{equation}{0}
\label{sec:thrmI_proof}
\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \underset{0 < \phi \leq 1}{\text{argmax}}\,
    \wt u(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \wt u(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    {\pd G(F) \over \pd \alpha}
    &=&
    {\pd \wt u(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    + {\pd \wt u(F, \phi) \over \pd \phi}(\alpha, K, \hat\phi)
    {\pd \hat\phi \over \pd \alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    {\pd \wt u(F, \phi) \over \pd \phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    {\pd \wt u(F, \phi) \over \pd \alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    {\pd \wt u(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    = {\partial \over \partial \alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously
  increasing with $X$. It follows
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd \alpha} \\
    &=& {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \log\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    {\pd \wt u(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for ${\pd G(F) \over \pd K}$, by the same argument as for
  ${\pd G(F) \over \pd \alpha}$, it suffices to show
  \[
  {\pd \wt u(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  {\pd \wt u(F, \phi) \over \pd K}(\alpha, K, \hat\phi)
  = {\partial \over \partial K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd K} \\
    &=& {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  {\pd \wt u(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}

>>>>

is not monotonic. To see this we may plug in \eqref{eq:hjyr} and
re-write the above as

@@

\subsection{Student's t-distributed equity return}
{\red This section is incomplete unless we can show results for $b>0$. Otherwise, we can do everything for $b=0$.} 
It is a common practice to use Student's t-distribution to model the
stationary distribution of equity returns. So it is of interest to
find out what implications this distribution has when it is combined
with the PDA preference. Formally we assume {\red instead of this function one can take a symmetric \ds\ with tails
$\P(X>x)=0.5 (\kappa/(x+\kappa))^{\alpha}$. If the symmetry causes another behavior than in the previous section this would be interesting.}
{\blue our tail index is always $\alpha$, not $\nu$.}
\[
f(x; \alpha) = c(\alpha) \left(
  1 + {x^2 \over \alpha}
\right)^{-(\alpha + 1)/2}
\]
where $\alpha > 1$ and
\[
c(\alpha) = {
  \Gamma({\alpha + 1 \over 2})
  \over
  \Gamma(\alpha/2) \sqrt{\alpha \pi}
}
\]
In the same way as for \eqref{eq:ipf}, we can write $\wt u(F, \phi)$
as
\begin{eqnarray}
  && \wt u(F, \phi) \nonumber \\
  &=&
  (1 + b)
  \int_{0}^{\infty}
  \underbrace{
    \left\{
      u(C(x)) \left[
        1 - {b \over 1 + b}\1_{\{x \ge q\}}
        \right]
      + u(C(-x))
    \right\}
  }_{U_{\text{all}}}
  f(x, \alpha) dx
  - b u(\delta v) F_X(q)
  \label{eq:t1}
\end{eqnarray}
where $C(\cdot)$ is defined in \eqref{eq:xxie1}. As shown in lemma
\ref{lemma:III}, when $b = 0$ and $u(\cdot)$
takes the power-form of \eqref{eq:hjyr}, $U_{\text{all}}$ is monotonic
depending on the values of $\xi$ and $(1 - \phi) e^r / \phi$. As given
in lemma \ref{lemma:II}, there is a point $x_0 > 0$ such that
${\pd f \over \pd \alpha}(x_0, \alpha) = 0$ and
$\forall x \in (0, x_0),
{\pd f \over  \pd \alpha}(x, \alpha) > 0$ and
$\forall x \in (x_0, \infty), {\pd f \over \pd \alpha}(x, \alpha) <
0$. Thus it remains to verify
$\int_0^\infty {\pd f \over \pd \alpha}(x, \alpha) dx < \infty$
if we are to apply lemma \ref{lemma:I}.

As computed in the proof of lemma \ref{lemma:II}, ${\pd f \over \pd
  \alpha}(x, \alpha)$ is given by \eqref{eq:xxie4.1}. It is also shown
there ${d \over d \alpha} c(\alpha) > 0$. Thus for
$\int_0^\infty {\pd f \over \pd \alpha}(x, \alpha) dx < \infty$
it suffices to show
\[
\int_ 0^\infty {
x^2
\over
(x^2 + \alpha) (1 + x^2 / \alpha)^{\alpha/2 + 1/2}
} dx < \infty
\]
We may write
\begin{eqnarray*}
&& \int_ 0^\infty {
x^2
\over
(x^2 + \alpha) (1 + x^2 / \alpha)^{\alpha/2 + 1/2}
} dx \\
&=& \left(\int_0^1 + \int_1^\infty \right) {
x^2
\over
(x^2 + \alpha) (1 + x^2 / \alpha)^{\alpha/2 + 1/2}
} dx \\
&=& I_1 + I_2
\end{eqnarray*}
Clearly
\[
I_1 < \int_0^1 {1 \over \alpha} dx < \infty
\]
while
\begin{eqnarray*}
  I_2 &=& \int_1^\infty {1 \over 1 + \alpha/x^2}
  {1 \over (1/x^2 + 1/\alpha)^{(\alpha+1) / 2}} {dx \over x^{\alpha +
      1}} \\
  &<& \int_1^\infty \alpha^{(\alpha+1) / 2} {dx \over x^{\alpha + 1}}
  < \infty
\end{eqnarray*}
So we conclude $\int_0^\infty {\pd f \over \pd \alpha}(x, \alpha) dx <
\infty$, and by lemma \ref{lemma:I}, $\wt u_{\text{max}}$ is monotonically
increasing/decreasing with $\alpha$ when $U_{\text{all}}(\cdot)$ is
monotonically decreasing/increasing.

@@

@@

\appendix
\section{A monontonicity lemma}
\setcounter{equation}{0}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x, \theta)$ parameterized by 
  $\theta \in \Theta \subseteq \mathbb R$ has support
  $(a, b) \subseteq \mathbb R$,
  and in addition $F(x, \theta)$ has density
  function $f(x, \theta)$ that is differentiable with respect to
  $\theta$ for all $\theta \in \Theta$.
  Let $X \sim F$ and assume function $h(\cdot)$ is defined on $(a, b)$
  and is monotonic throughout this interval.
  Moreover, we assume $h(x)$ and $f(x, \theta)$ satisfy
  \begin{equation}\label{eq:frt}
%    \E |h(X)| < \infty, \quad
    \int_a^b \left| {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty \text { and }
    \int_a^b \left| h(x) {\pd f(x, \theta) \over \pd \theta} \right| dx
    < \infty
  \end{equation}
  Then the following holds true:
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x, \theta) < 0$ for $x \in (a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x, \theta) > 0$ for $x \in (x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

\begin{proof}
  % Firstly we show, for any $S \subseteq (a, b)$,
  % \[
  %   {\pd \over \pd \theta} \int_S f(x, \theta) dx
  %   =
  %   \int_S {\pd \over \pd \theta} f(x, \theta) dx    
  % \]
  % Let
  % \[
  % f_{\Delta}(x, \theta) = {
  %   f(x, \theta +  \Delta) - f(x, \theta)
  %   \over
  %   \Delta
  % }
  % \]
  % Since $f(x, \theta)$ is differentiable for all $\theta \in \Theta$,
  % \[
  % f_{\Delta}(x, \theta) \to {\pd f \over \pd \theta}(x, \theta)
  % \quad \Delta \to 0
  % \]
  % For any give $\epsilon > 0$ and sufficiently small
  % $\Delta$, we have
  % \[
  % |f_{\Delta}(x, \theta)| <
  % \left|
  %     {\pd f \over \pd \theta}(x, \theta)
  % \right| (1 + \epsilon)
  % \]
  % Using \eqref{eq:frt} and dominated convergence theorem we obtain
  % \[
  % \lim_{\Delta \to 0} \int_S f_\Delta(x, \theta) dx
  % =
  % \int_S {\pd f \over \pd \theta}(x, \theta) dx
  % < \infty
  % \]
  % That is
  % \[
  %   {\pd \over \pd \theta} \int_S f(x, \theta) dx
  %   =
  %   \lim_{\Delta \to 0} {
  %     \int_S f(x, \theta + \Delta) dx
  %     -
  %     \int_S f(x, \theta) dx
  %     \over
  %     \Delta
  %   }
  %   =
  %   \int_S {\pd f \over \pd \theta}(x, \theta) dx     
  % \]
  % From \eqref{eq:frt} it easily follows that the set on which
  % ${\pd f(x, \theta) \over \pd \theta} = \infty$ has Lesbegue
  % measure 0. Call this set $S_0$.
  Firstly, by dominated convergence theorem, conditions \eqref{eq:frt}
  imply, for all $S \subseteq (a, b)$,
  \begin{eqnarray*}
    {\pd \over \pd \theta}\int_S f(x, \theta) dx
    &=&
    \int_S {\pd \over \pd \theta} f(x, \theta) dx \\
    {\pd \over \pd \theta}\int_S h(x) f(x, \theta) dx
    &=&
    \int_S h(x) {\pd \over \pd \theta} f(x, \theta) dx \\
  \end{eqnarray*}
  Thus we have
  \begin{eqnarray*}
    && {\pd \E h(X) \over \pd \theta} \\
    &=& \int_a^b h(x)
    {\pd f \over \pd \theta}(x, \theta) dx \\
    &=& \underbrace{\int_a^{x_0}
      h(x) {\pd f \over \pd \theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{x_0}^b
      h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_2}
  \end{eqnarray*}
  $x_0$ being located in the interior of $(a, b)$ and
  $h(\cdot)$ being monotonic imply $h(x_0) < \infty$.
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and ${\pd f \over \pd
    \theta}(x, \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_a^{x_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    Similarly, because ${\pd f \over \pd \theta}(x, \theta) < 0$ for
    $x \in (x_0, b)$ and $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b -h(x_0)
      \left|{\pd f \over \pd \theta}(x, \theta) \right| dx
      > -h(x_0)
      \int_{x_0}^b \left| 
        {\pd f \over \pd \theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      {\pd \E h(X) \over \pd \theta}
      > h(x_0) \int_a^b
      {\pd f \over \pd \theta}(x, \theta) dx
      = h(x_0) {\partial \over \partial \theta}
      \int_a^b f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    ${\pd f \over \pd \theta}(x_0, \theta) < 0$ on $(a, x_0)$  while
    ${\pd f \over \pd \theta}(x_0, \theta) > 0$ on $(x_0, b)$, 
    by similar arguments, one can show
    \[
    {\pd \E h(X) \over \pd \theta}> 0
    \]
\end{enumerate}
\end{proof}

@@

\section{Proof of Lemma~\ref{thrm:I}}
\setcounter{equation}{0}
\label{sec:thrmI_proof}
\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \underset{0 < \phi \leq 1}{\text{argmax}}\,
    \wt u(F_X, \phi)
  \end{equation}
  We have
  \[
  \tilde u_{\text{max}}(F_X) = \wt u(F_X, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    {d \tilde u_{\text{max}}(F_X) \over d \alpha}
    &=&
    \left.{\pd \wt u(\alpha, \phi) \over \pd \alpha}\right|_{\phi = \hat\phi}
    + \left.{\pd \wt u(\alpha, \phi) \over \pd \phi}\right|_{\phi = \hat\phi}
    {\pd \hat\phi \over \pd \alpha}
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies for all $\alpha$
  \begin{equation}
    \label{eq:xxie4}
    \left.{\pd \wt u(\alpha, \phi) \over \pd \phi}\right|_{\phi = \hat\phi} = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \left.{
        \pd \wt u(\alpha, \phi) \over \pd \alpha}
    \right|_{\phi = \hat\phi} &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    {\pd \wt u(\alpha, \phi) \over \pd \alpha}
    = {\partial \over \partial \alpha}\E[u((1 - \phi) e^r + \phi e^x) \1_{\{X < 0\}}]
  \end{eqnarray*}
  The function $u((1 - \phi) e^r + \phi e^x)$ is obviously
  increasing with $x$. It follows
  \begin{eqnarray*}
    && {\pd f_X(x; \alpha, K) \over \pd \alpha} \\
    &=& {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \log\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    {\pd \wt u(\alpha, \phi) \over \pd \alpha} &>& 0
  \end{eqnarray*}
  As for ${\pd \tilde u_{\text{max}}(F_X) \over \pd K}$, by the same argument as for
  ${\pd \tilde u_{\text{max}}(F_X) \over \pd \alpha}$, it suffices to show
  \[
  {\pd \wt u(K, \phi) \over \pd K} < 0
  \]
  We have
  \[
  {\pd \wt u(K, \phi) \over \pd K}
  = {\partial \over \partial K} \E \left[
    u((1 - \phi) e^r + \phi e^x) \1_{\{X < 0\}}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && {\pd f_X(x; \alpha, K) \over \pd K} \\
    &=& {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -K/\alpha$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-K/\alpha < x < 0$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  {\pd \wt u(K, \phi) \over \pd K} < 0  
  \]
\end{proof}
